\documentclass[12pt]{article}

% ---------- Packages ----------
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{hyperref}

% ---------- Shared footer + version control ----------
\input{tas-footer.tex}  % defines \fancypagestyle{tasfooter}

% ---------- Formatting ----------
\setstretch{1.15}
\setlist{nosep}

% ---------- Document ----------
\begin{document}

\pagestyle{tasfooter} % activate shared style for this document

\begin{center}
    {\LARGE \textbf{On-Site Alignment Checklist}}\\[0.25cm]
    {\large Technical Alignment Superhero (TAS)}
\end{center}

\vspace{0.5cm}
\tableofcontents
\newpage

% ===============================
% P1 — Must-Validate On-Site
% ===============================

\section*{P1 — Must-Validate On-Site}
\addcontentsline{toc}{section}{P1 — Must-Validate On-Site}

\subsection*{Mapped SOP Section: Step 4 — Onsite Validation and Discovery}

\begin{itemize}
    \item Validate server and endpoint inventory against ITGlue and Kaseya VSA.
    \item Confirm backup jobs have succeeded recently and review failures or anomalies.
    \item Confirm firewall make, model, and serial number onsite match documentation.
    \item Confirm switching infrastructure and upstream/downstream paths.
    \item Validate endpoint security coverage across devices (SentinelOne, Huntress, ThreatLocker, SaaS Alerts).
    \item Confirm primary and secondary ISP configuration (if applicable) and public IP details.
    \item Update ITGlue documentation for any discrepancies found onsite.
    \item Log onsite observations and risk findings in myITprocess.
    \item Create remediation tickets through myITprocess (syncing to BMS where applicable).
    \item Capture screenshots and photos as documentation evidence.
    \item Confirm alignment documentation is completed the same day as the onsite visit (unless leadership-approved exception).
\end{itemize}

\newpage

% ===============================
% P2 — Should-Validate On-Site
% ===============================

\section*{P2 — Should-Validate On-Site}
\addcontentsline{toc}{section}{P2 — Should-Validate On-Site}

\subsection*{Mapped SOP Sections: Step 4 — Onsite Validation and Discovery; Step 5 — Reporting and Recommendations}

\begin{itemize}
    \item Validate M365 MFA enforcement and privileged account roles.
    \item Validate lifecycle status of servers, workstations, and firewalls.
    \item Confirm unmanaged switches or guest networks are identified and documented.
    \item Review conditional access and baseline security configurations where applicable.
    \item Validate cabling and rack organization and note labeling improvements.
    \item Confirm SaaS Alerts configuration and reporting (if in scope).
\end{itemize}

\newpage

% ===============================
% P3 — Nice-to-Validate On-Site
% ===============================

\section*{P3 — Nice-to-Validate On-Site}
\addcontentsline{toc}{section}{P3 — Nice-to-Validate On-Site}

\subsection*{Mapped SOP Section: Step 6 — Follow-Up and Continuous Improvement}

\begin{itemize}
    \item Review Secure Score or similar security benchmark recommendations with an eye toward future improvements.
    \item Informally interview staff about recurring pain points or operational friction.
    \item Capture additional photos of cabling, closets, or other improvement opportunities.
    \item Inspect secondary wiring closets or remote areas if accessible and within scope.
    \item Identify unmanaged or vendor-owned infrastructure and ensure it is documented appropriately.
\end{itemize}

\end{document}
