\documentclass[12pt]{article}

% ---------- Packages ----------
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{hyperref}

% ---------- Shared footer + version control ----------
\input{tas-footer.tex}  % defines \fancypagestyle{tasfooter}

% ---------- Formatting ----------
\setstretch{1.15}
\setlist{nosep}

% ---------- Document ----------
\begin{document}

\pagestyle{tasfooter} % activate shared style for this document

\begin{center}
    {\LARGE \textbf{Pre-Visit Alignment Checklist}}\\[0.25cm]
    {\large Technical Alignment Superhero (TAS)}
\end{center}

\vspace{0.5cm}
\tableofcontents
\newpage

% ===============================
% P1 — Must-Do Pre-Visit Checklist
% ===============================

\section*{P1 — Must-Do Pre-Visit Checklist}
\addcontentsline{toc}{section}{P1 — Must-Do Pre-Visit Checklist}

\subsection*{Mapped SOP Sections: Step 2 — Client Planning and Scheduling; Step 3 — Pre-Visit Data Gathering}

\begin{itemize}
    \item Review ITGlue documentation for completeness and accuracy.
    \item Review ticket history in BMS (30--90 days) for recurring issues and trends.
    \item Review open risks and findings in myITprocess.
    \item Identify items requiring onsite validation or clarification.
    \item Confirm primary technical contact.
    \item Confirm business decision-maker (owner, Executive Director, COO, etc.).
    \item Confirm onsite access requirements (keys, rooms, VPN, escort).
    \item Validate monitored device inventory using Kaseya VSA.
    \item Validate backup status and health in Datto BCDR / Datto Backup for PCs.
    \item Review critical alerts (SentinelOne, Huntress, ThreatLocker, SaaS Alerts).
    \item Confirm scheduled visit date, time, and expected duration.
    \item Document the scheduled visit in myITprocess and internal calendar.
    \item Pre-fill alignment tool entries in myITprocess (Yes/No/Unknown).
    \item Prepare an onsite checklist or working document for live findings.
\end{itemize}

\newpage

% ===============================
% P2 — Should-Do Pre-Visit Checklist
% ===============================

\section*{P2 — Should-Do Pre-Visit Checklist}
\addcontentsline{toc}{section}{P2 — Should-Do Pre-Visit Checklist}

\subsection*{Mapped SOP Sections: Step 2 — Client Planning and Scheduling; Step 3 — Pre-Visit Data Gathering}

\begin{itemize}
    \item Review network diagrams in ITGlue and confirm recency.
    \item Validate lifecycle expirations based on known age data (workstations, servers, firewalls).
    \item Identify expected onsite attendees needed for system validation.
    \item Identify systems missing monitoring or security agents.
    \item Record assumptions that require onsite confirmation.
    \item Review tenant security posture (M365 configuration and high-risk settings).
\end{itemize}

\newpage

% ===============================
% P3 — Nice-to-Have Pre-Visit Checklist
% ===============================

\section*{P3 — Nice-to-Have Pre-Visit Checklist}
\addcontentsline{toc}{section}{P3 — Nice-to-Have Pre-Visit Checklist}

\subsection*{Mapped SOP Section: Step 2 — Client Planning and Scheduling}

\begin{itemize}
    \item Pre-draft observations or preliminary findings in myITprocess.
    \item Ask the client for planned business changes or upcoming initiatives.
    \item Request escalation or vendor contact information (if not already documented).
    \item Ask the client about recurring technology pain points or frustrations.
\end{itemize}

\end{document}
